### 2022-05-19 supplement.Rmd
Fix trace plot labels

```{r, figs3, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs3-caption)"}
# Extract convergence statistics (Rhat, Neff) from Bayesian results
conv_stats <- with(summary(res_meta), tibble(
  parameter = c(
    "b_Intercept", "sd_article__Intercept", "sd_article:experiment__Intercept"
  ),
  name_expr = c(
    "\"Hedges'\" ~ italic(g)",
    "italic(sigma)[article]",
    "italic(sigma)[experiment]"
  ),
  r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
  bulk_ess = print_big(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
  tail_ess = print_big(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
  r_hat_expr = str_c("italic(widehat(R)) ~ == ~ \"", r_hat, "\""),
  bulk_ess_expr = str_c("italic(N)[eff(bulk)] ~ == ~ \"", bulk_ess, "\""),
  tail_ess_expr = str_c("italic(N)[eff(tail)] ~ == ~ \"", tail_ess, "\""),
  y_pos = c(0.7, 0.75, 0.8)
))

>>>>

```{r, figs3, include=TRUE, fig.height=6, fig.width=12, fig.cap="(ref:figs3-caption)"}
# Extract convergence statistics (Rhat, Neff) from Bayesian results
conv_stats <- with(summary(res_meta), tibble(
  parameter = c(
    "b_Intercept", "sd_article__Intercept", "sd_article:experiment__Intercept"
  ),
  name_expr = c(
    "\"Hedges'\" ~ italic(g)",
    "italic(sigma)[article]",
    "italic(sigma)[experiment]"
  ),
  r_hat = print_num(c(fixed$Rhat, map_dbl(random, ~ .$Rhat)), digits = 4),
  bulk_ess = print_big(c(fixed$Bulk_ESS, map_dbl(random, ~ .$Bulk_ESS))),
  tail_ess = print_big(c(fixed$Tail_ESS, map_dbl(random, ~ .$Tail_ESS))),
  r_hat_expr = str_c("italic(widehat(R)) == \"", r_hat, "\""),
  bulk_ess_expr = str_c("italic(N)[eff(bulk)] == \"", bulk_ess, "\""),
  tail_ess_expr = str_c("italic(N)[eff(tail)] == \"", tail_ess, "\""),
  y_pos = c(0.7, 0.75, 0.8)
))
